DraftOne

### 2016-06-03 DraftOne.Rmd
Add function to simulate continuous exposure

```{r echo = FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(splines)
```

@@

```{r}
# A function for binary exposure which varies by season:
season_binexp <- function(n, p){
  p <- p #Change this later to reflect probability varying by season using trends
  binexp <- sample(c(0,1), size = n, replace = T, prob = c(1-p, p))
  return(binexp)
}

>>>>

```{r echo = FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(splines)
library(eesim)
```

@@

```{r}
# A function for binary exposure which varies by season:
season_binexp
